# Formatting Your Content - Markdown

Now we know which files to edit, but how can we edit these files? How do we format 

## Chapters

As mentioned earlier, headers are defined by a `#` before the title. Subheaders get increasingly more nested as add more `#` symbols before it. For example,

```
# Hello
```
would create a chapter title. Since there is only one `#` symbol, this would also create a new page. Again, try to keep only one chapter title per .Rmd file.

```
## Subheader
```
## Subheader

This is what a subheader would look like.

```
### Subheader
```
### Subheader

This is what a subheader with 3 `#` symbols would look like. You can add as many `#` symbols as you would like! There is also no limit to the the number of subheaders you can have. 

### An unnumbered subheader {-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the `{-}` at the end of the heading. For example, the above subheader was written like this:
```
### An unnumbered subheader {-}
```

## Cross-references {#cross}

Cross-references are ways to link to different to different parts of your workshop website.

### Chapters and sub-chapters

There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

2. The reference your text as follows `[any text you want can go here](#cross)`. This will end up looking like: [any text you want can go here](#cross).

## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Parts

Notice how index.Rmd in our CBW Bookdown template has `# (PART) Introduction {-}` (followed by `# Welcome`). This creates the "Introduction" section on the sidebar. 

There are already 2 main parts in the template: the introduction and modules sections.

If you want to add more parts, simply paste this: `# (PART) Introduction {-}` into a new .Rmd file, at the top of the file, before the main `# header`. 

## Footnotes

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## Citations (NOT SURE IF WE NEED WORKSHOPS NEED CITATIONS?)

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@xie2015] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>

## Equations

Here is an equation. Equations are written in latex.

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

You may refer to using `\@ref(eq:binom)`, like see Equation \@ref(eq:binom).

## Theorems and proofs

We also have specific syntax for theorems and proofs, for example, this code:

```
::: {.theorem #tri}
For a right triangle, if $c$ denotes the *length* of the hypotenuse
and $a$ and $b$ denote the lengths of the **other** two sides, we have
$$a^2 + b^2 = c^2$$
:::
```

produces

::: {.theorem #tri}
For a right triangle, if $c$ denotes the *length* of the hypotenuse
and $a$ and $b$ denote the lengths of the **other** two sides, we have
$$a^2 + b^2 = c^2$$
:::

Labeled theorems can be referenced in text using `\@ref(thm:tri)`, for example, check out this smart theorem \@ref(thm:tri).

You can learn more about this [here](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html)!

## Callout blocks (will be added later)

The R Markdown Cookbook provides more help on how to use custom blocks to design your own callouts: https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html


<!-- ## Metadata for sharing -->

<!-- Bookdown HTML books will provide HTML metadata for social sharing on platforms like Twitter, Facebook, and LinkedIn, using information you provide in the `index.Rmd` YAML. To setup, set the `url` for your book and the path to your `cover-image` file. Your book's `title` and `description` are also used. -->

<!-- This `gitbook` uses the same social sharing data across all chapters in your book- all links shared will look the same. -->

<!-- Specify your book's source repository on GitHub using the `edit` key under the configuration options in the `_output.yml` file, which allows users to suggest an edit by linking to a chapter's source file.  -->

