# How to Render/Compile Code {#render-code}

There are many ways to render and compile code using Bookdown!

Here are most of the "language engines" (programming languages) available to render, run and compile in Bookdown!

```{r}
names(knitr::knit_engines$get())
```
## Rendering Code

Just rendering code refers to Bookdown formatting code so that our users can view it. The code does not run or compile. This is very similar to what is shown in 020-module-1.Rmd of the bookdown template. An example is shown below.

````
```
insert code here
```
````

which appears as

```
insert code here
```

These are called "code chunks".

## Rendering Code with Highlights for Specific Languages

Bookdown also highlights (specific to the language) the outputted code for the ease of understanding. To do so, add the name of the language (of the many shown above) after the first  3 ``` ` ``` symbols. Note that the language is not case sensitive (so both "r" and "R" would render the same below). For example:

````
```r
x <- 42
x
```
````

renders into: 

```r
x <- 42
x
```

Notice that since `<-` is how to assign values to variables in R, it is highlighted. If we were to replace "r" with a different language, this may not be highlighted (depending if "<-" is a relevant symbol in that language.)

## Rendering and Compiling Code

To have the code actually compile, we need to put "{" and "}" brackets around the language, which we still put after the first 3 ``` ` ``` symbols. For example:

<!-- make the language some arbirtary language, since we just want to show what the code would look like -->

````{r, highlight=FALSE, eval=FALSE}
```{r}
x <- 42
x
```
````
````
renders and compiles into: 

```{r}
x <- 42
x
```

The second bar you see is the output of R command!

You can run these "code chunks" without previewing or building the book! To the right of your code chunk, there are 3 symbols (as seen below). 

<img src="https://docs.google.com/drawings/d/e/2PACX-1vSAWwloWK_sYRV44BYYCC2lhBpxLQQvkSYlJECfHnlYTwg7aPSPgOWuUfp_ybZQkAQ8QYSwUpH378Hv/pub?w=3763&amp;h=1237" alt="Picture of a R code chunk in RStudio">



A rectangular box will appear below your code chunk, with the output of your code. Plus, notice that in your bottom left window, any code you run also runs in your console. Both of these ways of checking your code happens for all languages! If you are previewing your book, you must re-preview it, since running the code becomes the new action for your console, instead of previewing the book.

:::: {.redbox data-latex=""}
::: {.center data-latex=""}
**Note!**
:::

If you want to run a certain language, you must have the language installed! R and python are already setup for you. (Python relies on the RStudio interface option, reticulate - you can reconfigure this if you'd like.) You may have to configure new languages so that they can run in RStudio, but generally, they should be able to run automatically.
::::

<p style="font-size: 8px;"></p>

:::: {.bluebox data-latex=""}
::: {.center data-latex=""}
**Exiting the Console**
:::

If you're running R, you don't have to exit the console (we already work in the R console when using Bookdown). However, if you're running a different language (for example, python), you will remain in the Python console, and must exit it to run Bookdown commands. You can look online for different ways to exit certain consoles, but generally running "quit" will return you to the R console.
::::


## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
