# Build Site

## How to edit _bookdown.yml
- add a new line, `output_dir: "docs"` to _bookdown.yml
- build the site
- add a `.nojekyll` file into the produced docs folder

## How to edit _output.yml (RC)
- after *before:* change your workshop name link
- after *edit:* put the link to the workshop repo, and end the link with `/%s`
- save


## Mandatory “index.Rmd” landing page

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading. 

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Build the book:
- “Build” button in RStudio IDE /OR/ bookdown::render_book()
- Preview the book: - updates on saves in viewer window bookdown::serve_book()

Before building 

### Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

### Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```

